### 2023-03-08 manuscript.tex
Trying @https to see if solves the problems we are having. [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/83d351133890f19b69d7c2fe2cf608d2bc773ceb.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/83d351133890f19b69d7c2fe2cf608d2bc773ceb/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366672176

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ddd995f3f5e7c62f7171b6281520a9be8cf82da1/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ddd995f3f5e7c62f7171b6281520a9be8cf82da1}{SORTEE-Github-Hackathon/manuscript@ddd995f}
on March 8, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/83d351133890f19b69d7c2fe2cf608d2bc773ceb/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/83d351133890f19b69d7c2fe2cf608d2bc773ceb}{SORTEE-Github-Hackathon/manuscript@83d3511}
on March 8, 2023.
